Increasing Chlorophyll *a* Amid Stable Nutrient Concentrations in Rhode Island Lakes and Reservoirs

### 2020-02-11 manuscript/peerj_preprint/manuscript.Rmd
closer for pre-print

![`r fig_num("ww_map", caption = "Map of URI Watershed Watch lake and reservoir sampling sites")`](../figures/ww_map.jpg)

@@

![`r fig_num("anomaly_schematic")`](../figures/anomaly_schematic.jpg)

@@

![`r fig_num(name = "temp_ri")`](../figures/ww_temp_trends_anomaly.jpg)

![`r fig_num(name = "chla_trend")`](../figures/paired_chla_trends_anomaly.jpg)

![`r fig_num(name = "tn_trend")`](../figures/paired_tn_trends_anomaly.jpg)

![`r fig_num(name = "tp_trend")`](../figures/paired_tp_trends_anomaly.jpg)

![`r fig_num(name = "np_trend")`](../figures/paired_np_trends_anomaly.jpg)

>>>>

![`r fig_num("ww_map", caption = "Map of URI Watershed Watch lake and reservoir sampling sites")`](../../figures/ww_map.jpg)

@@

![`r fig_num("anomaly_schematic")`](../../figures/anomaly_schematic.jpg)

@@

![`r fig_num(name = "temp_ri")`](../../figures/ww_temp_trends_anomaly.jpg)

![`r fig_num(name = "chla_trend")`](../../figures/paired_chla_trends_anomaly.jpg)

![`r fig_num(name = "tn_trend")`](../../figures/paired_tn_trends_anomaly.jpg)

![`r fig_num(name = "tp_trend")`](../../figures/paired_tp_trends_anomaly.jpg)

![`r fig_num(name = "np_trend")`](../../figures/paired_np_trends_anomaly.jpg)
